Measurement and Probability in Fuzzy Quantum Theories

### 2016-12-03 prop.tex
prop.lyx imported into LyX before drawing a table or graph...
prop.tex \section{Conclusion and Discussion} Organize the section, need to review how to write conclusion next time...

\documentclass{article}
\usepackage[ backend=biber]{biblatex}
\addbibresource{proposal/prop.bib}
\ExecuteBibliographyOptions{sorting=none,maxbibnames=5,doi=false,isbn=false,url=false}
\usepackage{fullpage}
\usepackage[utf8]{inputenc}
\usepackage{tensor}
\usepackage{url}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{bbm}
\usepackage{bbold}
\usepackage{wesa}
\usepackage{graphicx}

\theoremstyle{remark}
\newtheorem{example}{Example}
\newtheorem{definition}{Definition}
\newtheorem{cor}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{thm}{Theorem}
\newtheorem{case}{Case}
\newtheorem{conjecture}{Conjecture}
\newtheorem{problem}{Problem}
\newtheorem{claim}{Claim}

\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\events}{\ensuremath{\mathcal{E}}}
\newcommand{\qevents}{\ensuremath{\mathcal{E}}}
\newcommand{\pmeas}{\ensuremath{\mu}}
\newcommand{\imposs}{{\mbox{\wesa{impossible}}}}
\newcommand{\likely}{{\mbox{\wesa{likely}}}}
\newcommand{\unlikely}{{\mbox{\wesa{unlikely}}}}
\newcommand{\necess}{{\mbox{\wesa{certain}}}}
\newcommand{\overflow}{{\mbox{\wesa{overflow}}}}
\newcommand{\unknown}{{\mbox{\wesa{unknown}}}}
\newcommand{\bra}[1]{{\left\langle{#1}\right\vert}}
\newcommand{\ket}[1]{{\left\vert{#1}\right\rangle}}
\newcommand{\op}[2]{\ensuremath{\left\vert{#1}\middle\rangle\middle\langle{#2}\right\vert}}
\newcommand{\proj}[1]{\op{#1}{#1}}
\def\C{{\mathbb{C}}}
\newcommand{\ps}{\texttt{+}}
\newcommand{\ms}{\texttt{-}}
\newcommand{\ip}[2]{\ensuremath{\left\langle{#1}\middle\vert{#2}\right\rangle}}
\newcommand{\Tr}{\mathop{\mathrm{Tr}}\nolimits}
\newcommand{\rme}{\mathrm{e}}
\newcommand{\rmi}{\mathrm{i}}

\title{Measurement and Probability in Fuzzy Quantum Theories}
\date{\today}
\begin{document}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Intorduction}

@@

\begin{description}
\item[Research Question.] Confirm that as the number and
precision of the intervals increase the quantum interval-valued 
probability measure converges to the measure induced by the Born
rule. 
\end{description}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Proposal: General Plan}

A major aim of this proposal is to recast quantum probability and
measurement in a computational resource-aware setting. Our vision is
to unify the strands above in a novel way as explained in this
section. We start with some immediate observations that justify the
rest of the development.

\begin{itemize}

\item If we insist that probabilities cannot be computed to infinite
  precision and are bound to be approximations represented by
  intervals of confidence, then quantum states themselves can only be
  discussed within intervals of confidence. This raises an important
  philosophical question with immense practical relevance in the
  context of quantum computing. The question, which we could largely
  bypass in the classical case, is whether there is, in the background
  of all the measurements and probabilities, a ``real''
  infinitely-precise quantum state that is being approximated and
  that, in principle, can be more and more accurately described given
  more and more resources. In other words, does a Gleason,
  Bell~\cite{BellBook1987,Redhead1987-REDINA,peres1995quantum,Jaeger2007},
  or Kochen-Specker theorem still hold in a world with finite
  resources?  The answer will have to be \emph{no} if we are to
  respect these major theorems of quantum mechanics and quantum
  information. Thus our first radical departure from the conventional
  case will be that the quantum state itself must be fuzzy in some
  sense to be formalized.

\item Going further we actually have to concede not just the infinite
  accuracy of the quantum state, but its very existence as a ``real''
  entity that exists independently of measurements and
  probabilities. The reasons for this second radical position are as
  follows. First arguments embedded in the proof of the Kochen-Specker
  theorem essentially rule out the existence of a sample space as the
  probabilities of events cannot be consistently expressed using core
  assignments to elements of the sample space. Second, the frequency
  interpretation of probability which is already problematic in the
  classical case, becomes untenable in the quantum case. In both
  cases, but much more in the quantum case, it is much more sensible
  to interpret probability in the Bayesian sense as ``lack of
  knowledge''. This, and similar arguments elegantly expressed by
  recent work on Quantum Bayesianism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012},
  suggest that the quantum state is more like an interactive system in
  computer science parlance. In other words, the state is only
  determined by its interactions with the environment or observers. A
  rough but useful analogy in the context of computer science would be
  a web server: the state of such a system cannot be said to exist
  independently of the interactions with clients; each interaction
  with a client determines a future state of the system and may affect
  future interactions. Crucially, each client may have a
  \emph{different} view of the web server that is consistent with
  their own history of interactions. This computational perspective
  agrees with the philosophical position of QBism~\cite{VonBaeyer2016}
  that asserts that the quantum state is subjective: each observer has
  a different view of the quantum system that is consistent with their
  previous observations and that allows that observer, independently
  of other observers, to assign beliefs (i.e., probabilities) to
  possible future interactions.

\end{itemize}

The previous research question is essentially concerned with the
status of Gleason's theorem in a world with finite-precision
measurements. The following research questions are therefore natural
follow-up questions.

\begin{description}
\item[Research Question.] Investigate the status of the theorems
of Gleason, Bell, and Kochen-Specker for quantum interval-valued
probability measures. Revisit the Meyer-Mermin debate and its
generalizations in this mathematical framework.
\end{description}

>>>>

\documentclass{article}
\usepackage[ backend=biber]{biblatex}
\addbibresource{proposal/prop.bib}
\ExecuteBibliographyOptions{sorting=none,maxbibnames=5,doi=false,isbn=false,url=false}
\usepackage{fullpage}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{bbold}
\usepackage{wesa}
\usepackage{graphicx}

\theoremstyle{remark}
\newtheorem{example}{Example}
\newtheorem{definition}{Definition}
\newtheorem{thm}{Theorem}

\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\events}{\ensuremath{\mathcal{E}}}
\newcommand{\qevents}{\ensuremath{\mathcal{E}}}
\newcommand{\pmeas}{\ensuremath{\mu}}
\newcommand{\imposs}{{\mbox{\wesa{impossible}}}}
\newcommand{\likely}{{\mbox{\wesa{likely}}}}
\newcommand{\unlikely}{{\mbox{\wesa{unlikely}}}}
\newcommand{\necess}{{\mbox{\wesa{certain}}}}
\newcommand{\unknown}{{\mbox{\wesa{unknown}}}}
\newcommand{\ket}[1]{{\left\vert{#1}\right\rangle}}
\newcommand{\op}[2]{\ensuremath{\left\vert{#1}\middle\rangle\middle\langle{#2}\right\vert}}
\newcommand{\proj}[1]{\op{#1}{#1}}
\newcommand{\ps}{\texttt{+}}
\newcommand{\ms}{\texttt{-}}
\newcommand{\ip}[2]{\ensuremath{\left\langle{#1}\middle\vert{#2}\right\rangle}}
\newcommand{\Tr}{\mathop{\mathrm{Tr}}\nolimits}
\newcommand{\rme}{\mathrm{e}}
\newcommand{\rmi}{\mathrm{i}}

\begin{document}
\title{Measurement and Probability in Fuzzy Quantum Theories}
\date{\today}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion and Discussion}

If we insist that probabilities cannot be computed to infinite precision
and are bound to be approximations represented by intervals of confidence,
then quantum states themselves can only be discussed within intervals
of confidence. This raises an important philosophical question with
immense practical relevance in the context of quantum computing. The
question, which we could largely bypass in the classical case, is
whether there is, in the background of all the measurements and probabilities,
a ``real'' infinitely-precise quantum state that is being approximated
and that, in principle, can be more and more accurately described
given more and more resources. In particular, we could summarize our
examples and Gleason's theorem in table~\ref{table_long}. 
\begin{table}[ht]
\center{%
\begin{tabular}{c|cccc}
Measurement resources & Lowest & \multicolumn{2}{c}{$\longleftrightarrow$} & Highest\tabularnewline
\hline 
Number of intervals & $3$ & $4$ & \ldots{} & $\infty$\tabularnewline
\hline 
Maximum difference between ends of intervals & $1$ & $1/2$ & \ldots{} & $0$\tabularnewline
\hline 
Number of states in the core & 0 & 0 &  & 1\tabularnewline
\hline 
Number of states might corresponding to them & $3$ & $2$ & \ldots{} & $1$\tabularnewline
\hline 
How precise we could identify a state? & Coarse & \multicolumn{2}{c}{$\longleftrightarrow$} & Precise\tabularnewline
\end{tabular}}\caption{Summarize example~\ref{ex:three-dimensional-three-value} and \ref{ex:three-dimensional-4-value}
and Gleason's theorem}
\label{table_long}
\end{table}
Although the tend is clear, we still need more examples to fill the
blank and to prove our idea. Some research questions might be
\begin{description}
\item [{Research Question.}] Confirm that there is always an interval-valued
probability measure with an empty-core if the length of the interval
is bigger than zero. 
\item [{Research Question.}] In example~\ref{ex:three-dimensional-three-value}
and \ref{ex:three-dimensional-4-value}, we pick a possible candidate
corresponding to an interval-valued probability measure by only considering
the state whose interval-valued probability is $\necess$. Define
a general method which could be used to determine whether an interval-valued
probability measure is closer to the Born rule or not. 
\item [{Research Question.}] Confirm that as the number and precision
of the intervals increase the quantum interval-valued probability
measure converges to the measure induced by the Born rule. 
\end{description}
Since the validity of Gleason's theorem in a world with finite-precision
measurements is a question, the natural follow-up questions is to
investigate the status of the theorems of Bell~\cite{BellBook1987,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
and Kochen-Specker for quantum interval-valued probability measures
as well. Going further we actually have to concede not just the infinite
accuracy of the quantum state, but its very existence as a ``real''
entity that exists independently of measurements and probabilities.
The reasons for this second radical position are as follows. First
arguments embedded in the proof of the Kochen-Specker theorem essentially
rule out the existence of a sample space as the probabilities of events
cannot be consistently expressed using core assignments to elements
of the sample space. Second, the frequency interpretation of probability
which is already problematic in the classical case, becomes untenable
in the quantum case. In both cases, but much more in the quantum case,
it is much more sensible to interpret probability in the Bayesian
sense as ``lack of knowledge''. This, and similar arguments elegantly
expressed by recent work on Quantum Bayesianism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012},
suggest that the quantum state is more like an interactive system
in computer science parlance. In other words, the state is only determined
by its interactions with the environment or observers. A rough but
useful analogy in the context of computer science would be a web server:
the state of such a system cannot be said to exist independently of
the interactions with clients; each interaction with a client determines
a future state of the system and may affect future interactions. Crucially,
each client may have a \emph{different} view of the web server that
is consistent with their own history of interactions. This computational
perspective agrees with the philosophical position of QBism~\cite{VonBaeyer2016}
that asserts that the quantum state is subjective: each observer has
a different view of the quantum system that is consistent with their
previous observations and that allows that observer, independently
of other observers, to assign beliefs (i.e., probabilities) to possible
future interactions.
